Structured Versus Decorated Cospans

### 2022-03-23 cospans_new.tex
added Morgan Rogers to acknowledgements
gave online link to the paper on epidemic modeling

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/21 - dealing with referee's comments

@@

We thank Daniel Cicala, Brendan Fong and Joe Moeller for helpful conversations, and the referees for their many useful suggestions.  We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.   The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).

@@

\bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
algebraic framework for structured epidemic modeling.   To appear.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/23 - dealing with referee's comments

@@

We thank Daniel Cicala, Brendan Fong, Joe Moeller and Morgan Rogers for helpful conversations, and the referees for their many useful suggestions.  We especially thank Michael Shulman for suggesting a proof strategy that greatly improved this paper.   The third author would like to thank the General Secretariat for Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).

@@

\bibitem{BFMLP}  A.\ Baas, J.\ Fairbanks, M.\ Halter, S.\ Libkind and E.\ Patterson, An
algebraic framework for structured epidemic modeling.   Available at \href{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}{https://github.com/AlgebraicJulia/Structured-Epidemic-Modeling}.
